Computing Entropies with Nested Sampling

### 2019-01-16 talk/ms.tex
Extra image before movie
Minor updates

@@

{\color{blue}\url{http://www.mdpi.com/1099-4300/19/8/422}
\url{https://github.com/eggplantbren/InfoNest}}
\vspace{0.5cm}

@@

Ruth Angus (Flatiron Institute),
Ewan Cameron (Oxford), James Curran (Auckland), Tom Elliott (Auckland),
David Hogg (NYU), Kevin Knuth (SUNY Albany),
Thomas Lumley (Auckland),
Iain Murray (Edinburgh), John Skilling
(Maximum Entropy Data Consultants), Jared Tobin ({\tt jtobin.io}).

>>>>

\begin{center}
\includegraphics[width=0.7\textwidth]{movie/image000061.png}
\end{center}

@@

{\color{blue}
\url{http://www.mdpi.com/1099-4300/19/8/422} \\

\url{https://github.com/eggplantbren/InfoNest} \\

\url{https://github.com/eggplantbren/PosteriorEntropy}
}
\vspace{0.5cm}

@@

Ruth Angus (Flatiron Institute),
Ewan Cameron (Oxford), James Curran (Auckland), Tom Elliott (Auckland),
Dan Foreman-Mackey (Flatiron Institute),
David Hogg (NYU), Kevin Knuth (SUNY Albany),
Thomas Lumley (Auckland),
Iain Murray (Edinburgh), John Skilling
(Maximum Entropy Data Consultants), Jared Tobin ({\tt jtobin.io}).
